\sysfull

### 2017-08-12 paper/coalescing.tex

\sys determines $C$ for a given operation based on the number of tasks completed, $S$, during the last operational period. \sys begins execution in a coalesced task with an infinite $C$ value. With a continuous power supply, the system executes from the start with all tasks as coalesced tasks entirely avoiding the cost of committing state. On intermittent power, the system executes a sequence of tasks that is interrupted by a power failure. \sys explicitly tracks $S$ during the previous operating period. \sys assigns $C$ to be equal to half of the value of $S$. If more tasks in total are able to complete in an operating period, \sys attempts to coalesce more tasks during the next operating period. If fewer tasks complete, \sys attempts to coalesce fewer tasks during the next operating period. $S$ includes the count of both coalesced and committing tasks completed. If no committing task completes, i.e., execution does not make progress, \sys updates $S$ and attempts to coalesce fewer tasks during the next operating period.

@@

\noindent\textbf{Task Coalescing Illustration:} Figure~\ref{fig:coalescing_example_states} (left) shows a sequence of three tasks executing in \sys with no coalescing, incurring the cost of commit at each task transition. The same figure shows the same sequence of tasks executing as coalesced groups of three tasks $C=2$ (center) and $C=3$ (right). Figure~\ref{fig:coalescing_example_flowchart} shows how \sys adapts the value of $C$ based on $S$. \sys executes tasks in the first operating period, assigning the \emph{half of sum of all previous $S$ periods} (in the example case: $C=8/2$). \sys completes then coalesced tasks successfully (four tasks were executed) and in the next operating period, i.e. $C=(8+4)/2$. In the third task execution, power fails after the second task. Then \sys re-executes coalesced task since the previous failure and sets $C=(6+8+2)/2$ in the next operating period. If a larger number of tasks successfully complete in the next operating period, i.e., $S$ is larger, $C$ correspondingly increases, allowing more aggressive coalescing.

>>>>

\sys determines $C$ for a given operation based on the number of tasks
completed, $S$, during the current operational period. \sys begins execution in
a coalesced task with $C$ initialized to half of the number of tasks executed
during the previous operating period and $S$ initialized to $0$. The system
executes $C-1$ coalesced tasks followed by one committing task. After each
commit, \sys assigns $C$ to half of $S$.   If more tasks complete in an
operating period, \sys attempts to coalesce more tasks. If fewer tasks
complete, \sys attempts to coalesce fewer tasks. If no committing task
completes due to a power failure, \sys updates $C$ on reboot to half of $S$
(the number of tasks completed before the power failure) and continues.

@@

\noindent\textbf{Task Coalescing Illustration:}
Figure~\ref{fig:coalescing_example_states} shows a sequence of three tasks
executing in \sys. At left, there is no coalescing and tasks incur the cost of
commit at each transition. The center shows the same tasks executing as
coalesced groups of two tasks $C=2$, avoiding one commit.  At right, \sys
coalesces three tasks ($C=3$) avoiding two commits.
Figure~\ref{fig:coalescing_example_flowchart} shows how \sys adapts the value
of $C$ based on $S$. \sys executes tasks in the first operating period, with
$C$ equal to half the number of tasks completed in the prior execution period.
In the example, $C$ starts at eight. After completing eight tasks, \sys commits
and reduces $C$ by half to four.  \sys completes two of four tasks and power
fails.  During the operating period, \sys executed a total of ten tasks (i.e.,
$S=10$) and when \sys restarts, $C$ is assigned to five (i.e., half of $S$).
\sys completes the five coalesced tasks $S=5$ and after committing, assigns $C$
to half of $S$, which is three (after rounding up). \sys coalesces three tasks
and again commits.  At this point, $S=8$; \sys assigns $C=4$ and execution
continues.

### 2017-08-12 paper/evaluation.tex

\subsection{Methodology}
\label{sec:results_hardware}

We evaluated \sys using a WISP\,5.1~\cite{wisp5,wisp} energy-harvesting
platform build around a MSP430FR5969~\cite{wolverine} MCU with 64kB of FRAM.
We used a TI Flash Emulation Tool (FET)~\cite{fet} as a power supply during
experiments with continuous power.  For energy measurements, we used
EDB~\cite{edb}.  In experiments with wireless power, we powered the WISP using
an RFID reader (Impinj R1000 with firmware version
3.2.4.240~\cite{r1000_data_sheet}) connected to the Liard RFMAX S9028PCRJ
8\,dBic~\cite{atlas2015}. We ccontrolled the RFID reader from a workstation
running Ubuntu 10.4 using \emph{sllurp}~\cite{sllrp_github}.  We set the
transmitted power of the RFID reader to 30\,dBm at 915\,MHz center frequency.
For distance-controlled experiments, we affixed the WISP at varying lengths to
hollow paper tubes placed flat on a lying antenna. We did timing measurements
using the Salea~\cite{saleae} logic analyzer.

>>>>

\subsection{Hardware Suite Description}
\label{sec:results_hardware}

In all experiments we used the following computing hardware: WISP\,5.1~\cite{wisp5,wisp} build around MSP430FR5969~\cite{wolverine} 64\,kB FRAM microcontroller. WISP\,5.1 has been re-programmed during experiments using TI's Flash Emulation Tool (FET)~\cite{fet} with TI Code Composer Studio version 7. FET was also used as a power supply in non-intermittent power experiments. Energy consumption measurements provided in eariler sections were done with Carnegie Mellon's EDB~\cite{edb}. In experiments involving wireless power, the WISP was powered through an RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to the Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. The RFID reader is controlled by a PC running Ubuntu 10.4 executing an open source Python-based \emph{sllurp} library~\cite{sllrp_github}. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance-controlled experiments, the WISP was positioned at varying length hollow paper tubes placed directly on a flat lying antenna. Code execution times were measured using Salea~\cite{saleae} logic analyzer.
